Implementing simplified INLA into `aghq`

### 2022-12-17 src/dev_sinla/sinla.Rmd
Small bug in dev_sinla

#' The log-probabilities at the set of input values
lps <- sapply(spline_nodes(modesandhessians, i = 1, k = 7), gaussian_marginal)

plot_marginal_spline <- function(lps) {
  #' Build a Lagrange polynomial interpolant of the marginal posterior
  ss <- splines::interpSpline(gg$nodes, lps, bSpline = TRUE, sparse = TRUE)
  interpolant <- function(x) { as.numeric(stats::predict(ss, x)$y) }
  finegrid <- seq(-5, 5, by = 0.1)
  df <- data.frame(x = finegrid, y = exp(interpolant(finegrid)))

@@

plot_marginal_spline(lps)
```

@@

lps <- sapply(gg$nodes, old_laplace_marginal)
plot_marginal_spline(lps)
```

@@

lps <- sapply(gg$nodes, laplace_marginal)
plot_marginal_spline(lps)
```
## Full Laplace method (new new method)

@@

lps <- sapply(gg$nodes, new_laplace_marginal, i = 1)
plot_marginal_spline(lps)
```
Now let's loop this over $i$ so we can compare to the other methods.
The hypothesis is that this will be better than the empirical Bayes methods.

>>>>

#' The log-probabilities at the set of input values
nodes <- spline_nodes(modesandhessians, i = 1, k = 7)
lps <- sapply(nodes, gaussian_marginal)

plot_marginal_spline <- function(nodes, lps) {
  #' Build a Lagrange polynomial interpolant of the marginal posterior
  ss <- splines::interpSpline(nodes, lps, bSpline = TRUE, sparse = TRUE)
  interpolant <- function(x) { as.numeric(stats::predict(ss, x)$y) }
  finegrid <- seq(-5, 5, by = 0.1)
  df <- data.frame(x = finegrid, y = exp(interpolant(finegrid)))

@@

plot_marginal_spline(nodes, lps)
```

@@

lps <- sapply(nodes, old_laplace_marginal)
plot_marginal_spline(nodes, lps)
```

@@

lps <- sapply(nodes, laplace_marginal)
plot_marginal_spline(nodes, lps)
```

## Full Laplace method (new new method)

@@

lps <- sapply(nodes, new_laplace_marginal, i = 1)
plot_marginal_spline(nodes, lps)
```
Now let's loop this over $i$ so we can compare to the other methods.
The hypothesis is that this will be better than the empirical Bayes methods.
